ShrinkNets: Learning Network Size while Training

### 2018-02-10 paper/ICML/evaluation.tex
Update evaluation.tex
small fix
edits

Note that the best performing \shrink model has $92.07\%$ accuracy which
is identical to the accuracy of the static network, while the \shrink model
is $2.22$ times smaller. In addition, if we give up just 1\% error, \shrink
find a model that is 35.5 times smaller than any static network that performs
as good or better.

@@

Note that the best performing \shrink models has $96.91\%$ accuracy while the
best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
times smaller. In addition, if we give up just 0.5\% error, \shrink find a
model that is 38.6 times smaller than any static network with equivalent accuracy.

>>>>

Note that the best performing \shrink model has $92.07\%$ accuracy which
is identical to the accuracy of the static network, while the \shrink model
is $2.22$ times smaller. In addition, if we give up just 1\% error, \shrink
find a model that is 35.5 times smaller than any static network that performs
as good.

@@

Note that the best performing \shrink models has $96.91\%$ accuracy while the
best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
times smaller. In addition, if we give up just 0.5\% error, \shrink find a
model that is 38.6X smaller than any static network with equivalent accuracy.
